---
title: "Dataset Summary"
author: "YOUR NAMES HERE"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
```


```{r, message = FALSE}
# delete all but the one for your dataset
measles <- read_csv(here("Data", "measles.csv"))
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
video_games <- read_csv(here("Data", "video_games.csv"))
```

## Overall Summary

```{r}
_______ %>% summary()

```

* How many observations are in this dataset?

[YOUR ANSWER HERE]

* How many variables are in this dataset?  Which are quantitative, and which are categorical?

[YOUR ANSWER HERE]

* Is there any missing data in this dataset?

[YOUR ANSWER HERE]


## Quantitative Variables

Choose two quantitative variables in your dataset.

For each, provide the *median and IQR* and a *boxplot* by filling in the blanks below with your dataset name and your variable name.

```{r}
_________ %>%
  summarize(median(______),
            IQR(______))

_________ %>%
  ggplot() +
  geom_boxplot(aes(x = _______))
```

Then, for each, provide the *mean and standard deviation* and a *histogram*:

```{r}
_________ %>%
  summarize(mean(______),
            sd(______))

_________ %>%
  ggplot() +
  geom_histogram(aes(x = _______))
```


Comment on the results.  What is the **shape** of the distribution?  Are the mean and median the same, or different, and what does that tell you about the data?  Do you notice anything interesting or unusual?

## Quantitative Variables

Now choose a **categorical** variable in your dataset, and *one* of the quantitatives from above.

For each category, provide the *median and IQR* and a *side-by-side boxplot* by filling in the blanks below with your dataset name and your variable names.

```{r}
_________ %>%
  group_by(____) %>%
  summarize(median(______),
            IQR(______))

_________ %>%
  ggplot() +
  geom_boxplot(aes(y = _______,
                   x = _______))
```

Then, for each category, provide the *mean and standard deviation* and a *histogram*:

```{r}
_________ %>%
  group_by(_____) %>%
  summarize(mean(______),
            sd(______))

_________ %>%
  ggplot() +
  geom_histogram(aes(x = _______,
                     fill = _____),
                 alpha = 0.5)
```


Comment on the results.  Do you think there is evidence that this quantitative variable is different across the categories?  Why or why not?

## Research Questions

Come up with three interesting research questions that you think could be addressed with this dataset.