---
title: "Confidence Intervals, Central Limit Theorem"
author: "YOUR NAME HERE"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
library(infer)
```


```{r, message = FALSE}
# delete all but the one for your dataset
measles <- read_csv(here("Clean Data", "measles_clean.csv"))
wine_ratings <- read_csv(here("Clean Data", "wine_ratings_clean.csv"))
video_games <- read_csv(here("Clean Data", "video_games_clean.csv"))
```

## Part One: Normality

*(Hint: You should copy your code over from a previous project step!)*

Choose a **quantitative** variable in your dataset.  Make a histogram of this
variable, and comment on it.  Does it seem to be Normally distributed?

```{r}

```

Find the *sample mean* and *sample sd* of the variable.

```{r}

```

If your variable were Normally distributed, 95\% of the observations would 
fall between what two values?  (Use R as a calculator for this.)


```{r}

```

In reality, 95\% of your observations fall between...

```{r}
_______ %>%
  summarize(quantile(_____, c(0.025, .975))
```

Did this change your thoughts about whether the variable is Normal?

## Part Two: Conf Ints

Make a 95\% confidence interval for the **true mean** of your variable.  (Use R as
a calculator to do this.)

```{r}

```

But wait!  It's the 21st century.  We have computers.  Let's make the computer
do all the work for us.

```{r}
_____ %>%
  t_test(______, mu = 0)
```

Based on this output, what is the 95\% confidence interval?

Now make a 99\% confidence interval:

```{r}
_____ %>%
  t_test(______, mu = 0, conf_level = _____)
```

Based on these outputs, what are the chances of seeing a sample mean of _____, if
the true mean is 0?

Make a more reasonable guess about the true mean (but you should not guess your 
sample mean exactly).  What are the chances of seeing a sample mean of _____, if
the true mean is _____?

```{r}
_____ %>%
  t_test(______, mu = 0)
```


## Part Three:  Compare two categories.

Now choose a *categorical* variable and (temporarily) narrow it down to only
two categories:

```{r}
______temp <- ______ %>%
  filter(______ %in% c("______", "_______"))
```

Calculate the *sample means* in each category:

```{r}
_____ %>%
  group_by(_____) %>%
  summarize(mean(______))
```

What is the difference in sample means?


Let's make a confidence interval for the **true difference in means** across these
two categories:

```{r}
_____ %>%
  t_test(______ ~ _______)
```

Which category had the **bigger** sample mean?

Interpret your interval:  "I am 95\% confident that...."

If these two categories have equal **true means**, what are the chances of getting
a difference of sample means of ______?


Do you believe these categories have equal true means, or not?  What do you
conclude about the real world?





