---
title: "Data Cleaning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
```

## Load and examine the data

```{r, message = FALSE}
# delete all but the one for your dataset
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
head(wine_ratings)
```

## Select variables and drop NAs


```{r}
______ <- ______ %>%
  select(________)
```

```{r}
______ <- ______ %>% drop_na()
```

## Clean quantitative variables

```{r}
______ <- ______ %>%
  filter(________ < ______)
```


## Clean categorical variables

(For each variable, choose only **one** of the three cleaning options!)

```{r}
______ <- ______ %>%
  mutate(
    ______ = fct_other(keep = ________)
  )
```

```{r}
______ <- ______ %>%
  filter(
    _______ %in% c("______", "_______")
  )
```

## Check your work

Look at the summary of your clean data.  Does it look how you hoped?

```{r}
_____ %>% summary()
```


## Visualization

Make some visualizations, to see if your variables are now cleaned up and
able to answer research questions.

(Copy-pasting these from other steps is encouraged!)


## Save final dataset

This will make a new text file named "data_final.csv", which contains the newly
cleaned-up dataset!

```{r, message = FALSE}
## write in the name of your clean dataset
_______ %>% write_csv(here("Data", "data_final.csv"))

```