---
title: "Visualization"
author: "YOUR NAMES HERE"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
```


```{r, message = FALSE}
# delete all but the one for your dataset
prison_pop <- read_csv(here("Data", "prison_population.csv"))
cetaceans <- read_csv(here("Data", "cetaceans.csv"))
measles <- read_csv(here("Data", "measles.csv"))
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
video_games <- read_csv(here("Data", "video_games.csv"))
```

## Research question: Cat-Cat

Choose a research question that pertains to the *relationship* between two *categorical* variables.

Create a visualization that addresses this research question.  Briefly interpret your results.

```{r}
_______ %>%
  ggplot() +
  geom_bar(aes(x = _______, fill = _____),
           position = ________)
```


## Research question: Quant-Quant

Choose a research question that pertains to the *relationship* between a *categorical* variable and a *quantitative variable*.

Create a visualization that addresses this research question.  Briefly interpret your results.

```{r}
_______ %>%
  ggplot() +
  geom_point(aes(x = _______, y = _____))

```


## Research question: Cat-Quant

Choose a research question that pertains to the *relationship* between two *quantitative* variables.

Create a visualization that addresses this research question.  Briefly interpret your results.

```{r}
_______ %>%
  ggplot() +
  geom_boxplot(aes(x = _______, y = _____))

_______ %>%
  ggplot() +
  geom_density(aes(x = _______, fill = _______))
```
