---
title: "Visualization"
author: "YOUR NAMES HERE"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
```


```{r, message = FALSE}
# delete all but the one for your dataset
prison_pop <- read_csv(here("Data", "prison_population.csv"))
cetaceans <- read_csv(here("Data", "cetaceans.csv"))
measles <- read_csv(here("Data", "measles.csv"))
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
video_games <- read_csv(here("Data", "video_games.csv"))
```


Return to your three research questions from last week.

Provide the *visualization* from the previous lab, as well as any relevant *summary statistics* for these two variables.

Discuss your results in the context of the *variability* of the data:

* What would you expect to see in the visual and summaries if the answer to your research question was *yes*?

* What would you expect to see in the visual and summaries if the answer to your research question was *no*?

* What conclusion do you think this data supports?
