---
title: "The Normal Distribution"
author: "YOUR NAMES HERE"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
```


```{r, message = FALSE}
# delete all but the one for your dataset
prison_pop <- read_csv(here("Data", "prison_population.csv"))
cetaceans <- read_csv(here("Data", "cetaceans.csv"))
measles <- read_csv(here("Data", "measles.csv"))
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
video_games <- read_csv(here("Data", "video_games.csv"))
```

Choose two quantitative variables from your dataset.

For each:

1. Make a histogram or density of the data.

```{r}

```


2. Find the *sample mean* and *sample sd* of the variable.

```{r}

```


3. Find the *25th and 75th percentiles* for the observed values of this variable:

```{r}
______ %>%
  summarize(
    quantile(______, c(0.25, 0.75))
  )
```

4. Find the *25th and 75th percentiles* of a **Normal Distribution** with the same mean and sd as the variable.

```{r}
qnorm(0.25, mean = _____, sd = _____)
qnorm(0.75, mean = _____, sd = _____)
```

5. Based on your answers to 3 and 4, as well as your histogram, do you think this variable is normally distributed?

6. Make a qq-plot for this variable.  What does it suggest about the *distribution* of the variable?

```{r}
________ %>%
  ggplot() +
  geom_qq(aes(sample = _______))
```



