---
title: "Visualization"
author: "YOUR NAMES HERE"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
```


```{r, message = FALSE}
# delete all but the one for your dataset
prison_pop <- read_csv(here("Data", "prison_population.csv"))
cetaceans <- read_csv(here("Data", "cetaceans.csv"))
measles <- read_csv(here("Data", "measles.csv"))
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
video_games <- read_csv(here("Data", "video_games.csv"))
```


## Evidence: Cat-Cat

Return to your research question (or choose a new one) pertaining to two categorical variables.  You'll want to choose variables with a small number of categories.  You may wish to combine categories using the following code:

```{r}
_______ <- _______ %>%
  mutate(
    _______ = fct_lump(______)
  )
```

1.  Show the *counts* for each category.

```{r}

```



2.  Calculate the *expected counts* for each category.  Use R to do this, and show your work:

```{r}

```


3. Discuss the difference between the expected and actual counts.  Do you think there is a relationship between these variables?


## Evidence: Quant-Quant

Return to your research question (or choose a new one) pertaining to a two quantitative variables.

1. Calculate the *correlation* or the *covariance*  (your choice) of the quantitative variable within each category.

```{r}
_______ %>%
  group_by(_______) %>%
  summarize(_______)

```

2. Run this code to make a *shuffled* version of your quantitative variable:

```{r}
set.seed(24892)  ## don't worry about this part!

_______ <- ______ %>%
  mutate(
    quant_shuffled = sample(_______)
  )
```

3. Calculate the *correlation* or the *covariance* of the *shuffled* quantitative variable, within each category.

```{r}
_______ %>%
  group_by(_______) %>%
  summarize(_______)

```

4. Repeat steps 2 and 3 a total of 5 times. (Copy paste the code, except for the `set.seed` part, five times - don't just hit the "play" button over and over!)

```{r}
set.seed(24892)  ## don't worry about this part!

______ %>%
  mutate(
    quant_shuffled = sample(_______)
  ) %>%
  group_by(_______) %>%
  summarize(_______)
```

5. Comment on the *actual* correlation/covariance in the data versus the correlation/covariance in the *shuffled* data.  Do you think there is evidence that there is a relationship between these quantitative variables?




## Evidence: Cat-Quant

Return to your research question (or choose a new one) pertaining to a categorical variable and a quantitative variable.  You'll want to choose a categorical variable with a small number of categories.

1. Calculate the *mean* or the *median*  (your choice) of the quantitative variable within each category.

```{r}
_______ %>%
  group_by(_______) %>%
  summarize(_______)

```

2. Run this code to make a *shuffled* version of your quantitative variable:

```{r}
set.seed(24892)  ## don't worry about this part!

_______ <- ______ %>%
  mutate(
    quant_shuffled = sample(_______)
  )
```

3. Calculate the *mean* or the *median* of the *shuffled* quantitative variable, within each category.

```{r}
_______ %>%
  group_by(_______) %>%
  summarize(_______)

```

4. Repeat steps 2 and 3 a total of 5 times. (Copy paste the code, except for the `set.seed` part, five times - don't just hit the "play" button over and over!)

```{r}
set.seed(24892)  ## don't worry about this part!

______ %>%
  mutate(
    quant_shuffled = sample(_______)
  ) %>%
  group_by(_______) %>%
  summarize(_______)
```

5. Comment on the *actual* difference of means/medians in the data versus the difference of means/medians across categories in the *shuffled* data.  Do you think there is evidence that there is a relationship between the categorical and quantitative variables?