---
title: "Dataset Overview"
author: "YOUR NAME HERE"
output: html_document
---


```{r, include = FALSE}
## Ignore this for now; just hit "play"

library(tidyverse)
library(here)
library(tidymodels)
library(janitor)
library(gtsummary)
```

## Overview and purpose

Describe the context of your dataset.  What general problem or topic is being studied?  Why might people be interested in this topic?

## Source

Describe the source of your dataset.  Who collected/created it?  Who funded it?

## Information

Describe the information contained in the dataset.  What was recorded?  How was it measured?  What are the observational or experimental units?  What are the variables?  Are they quantitative, categorical, or neither?


## Related information

Can you find any places where your dataset has been analyzed before?

Can you find any related datasets that might be interesting to combine with this one?

Can you find any scientific articles that relate to your dataset?

## Load the data

Choose your dataset, and delete the extra lines:

```{r, message = FALSE}
# delete all but the one for your dataset
measles <- read_csv(here("Data", "measles.csv"))
wine_ratings <- read_csv(here("Data", "wine_ratings.csv"))
video_games <- read_csv(here("Data", "video_games.csv"))
```

Look at some information about your dataset:


```{r}
_____ %>% head()
_____ %>% summary()
```

#### Planning ahead

What are some possible issues you see with this dataset, that might make it difficult to analyze?


# Your Project Step

Fill out this R Markdown file for **one** of the three dataset options.   Make sure that you write the file in "essay form" - that is, you should write in complete sentences, and the prompt questions should be deleted.

Knit the file, export it, and upload it to Canvas.

(See "How to turn in your file" if you don't remember how to export!)